Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-15 aistats.tex
Cleanup end of optimization

To analyze stochastic algorithms, one also need to quantify the randomness.
While many assumptions exist for SGD \citep[\S3 for a modern review]{khaled2020better}, only a few have been adapted to SMD with relative smoothness \citep{hanzely2018fastest, dragomir2021fast, dorazio2021stochastic}, but they have so far been lacking concrete examples.
We review these analyses in the light of the MAP and provide a summary in \cref{tbl:assumptions}.

@@

\subsubsection{Bounded Optimality Gap}
Inspired by \citet{loizou2021stochastic}, \citet{dorazio2021stochastic} explore the hypothesis
\alignn{
\min_\nat f(\nat) - \expect[X]{\min_\nat f_X(\nat)} \leq C,
\label{eq:dorazio}
}
where $f_X$ is a stochastic estimate of $f = \expecti{f_X}$. In our case $f_X(\nat) = - \log p(X\cond \nat)$.
In other words, this lower bounds the expectation of the minimum of the stochastic estimates.
For probabilistic models, such a bound is finite as soon as the model cannot give infinite density to any data point $x$.
This holds, for instance, for discrete distributions because the probability mass is upper bounded by $1$; however, it rules out  many families.
In the case of normal distributions$\cN(m, \sigma^2)$, setting $\mu=x$ and $\sigma^2 \rightarrow 0$ gets $p_\nat (x) \rightarrow +\infty$. We have a similar behavior for gamma distribution with $\alpha = \beta x$ and $\beta \rightarrow +\infty$, or with the beta distribution with $\alpha=\beta \frac{x}{1-x}$ and $\beta \rightarrow +\infty$.
 Other counter-examples include inverse Gaussians, log-normal, gamma, inverse gamma.

@@

If assumptions~\eqref{eq:hanzely} and~\eqref{eq:dragomir} do not hold for every iterate, then let us assume they hold on average. Does the proof remain valid? Yes, I think so \TODO{check this}. Does it become impossible to prove / as hard as the initial problem? Yes.
\TODO{Does it match exactly the variance from the bias-(mixed)-variance decomposition ?}

>>>>

To analyze stochastic algorithms, one also need to quantify the randomness of stochastic gradients $g(\nat)$ .
While many assumptions exist for SGD \citep[\S3 for a modern review]{khaled2020better}, only a few have been adapted to SMD with relative smoothness \citep{hanzely2018fastest, dragomir2021fast, dorazio2021stochastic}, but they have so far been lacking concrete examples.
We review these analyses in the light of the MAP and provide a summary in \cref{tbl:assumptions}.

@@

\subsubsection{Bounded Optimality Gap}
Inspired by \citet{loizou2021stochastic}, \citet{dorazio2021stochastic} explore the hypothesis
\alignn{
\min_\nat f(\nat) - \expect[X]{\min_\nat f_X(\nat)} \leq C,
\label{eq:dorazio}
}
where $f_X$ is a stochastic estimate of $f = \expecti{f_X}$. In our case $f_X(\nat) = - \log p(X\cond \nat)$.
In other words, this lower bounds the expectation of the minimum of the stochastic estimates.
For probabilistic models, such a bound is finite as soon as the model cannot give infinite density to any data point $x$.
This holds, for instance, for discrete distributions because the probability mass is upper bounded by $1$; however, it rules out  many families.
In the case of normal distributions $\cN(m, \sigma^2)$, setting $m=x$ and $\sigma^2 \rightarrow 0$ gets $p_\nat (x) \rightarrow +\infty$. We have a similar behavior for gamma distribution with $\alpha = \beta x$ and $\beta \rightarrow +\infty$, or with the beta distribution with $\alpha=\beta \frac{x}{1-x}$ and $\beta \rightarrow +\infty$.
 Other counter-examples include inverse Gaussians, log-normal, gamma, inverse gamma.

@@

%\rlp{Add discussion here.}
